Effects of Weather on Maize Yield in Kenya

### 2019-01-16 presentations/January2019/presentation4.tex
presentation

\begin{enumerate}
\item Arid and semi-Arid (ASAL): bi-modal
	\begin{itemize}
	\item MAM and OND
	\item \textcolor{red}{Short and Long rains}
	\end{itemize}
\item non-ASAL: uni-modal
	\begin{itemize}
	\item March to August
	\end{itemize}

@@

\begin{frame}\label{Intro-Approaches}
\frametitle{Intro-Approaches}

@@

\begin{frame}
       \hspace{-0.8cm}  \textbf{NDMA Early Warning Phase\\ \hspace{-0.8cm} Classification}

@@

\vspace{-1.3cm}
    \begin{figure}
      \begin{columns}
        \column{.5\linewidth }

  \vspace{-1.8cm}        
        \column{.5\linewidth}

  \hspace{-2.6cm}  \includegraphics[width = 1.2\textwidth]{PrecNA.png}  %565*238
      \end{columns}
    \end{figure}

@@

\begin{frame}\label{Data}
\frametitle{Data}

\begin{itemize}
\item Maize yields
\begin{itemize}
\item source: Famine Early Warning Systems Network (FEWS NET)
\item County level, yearly, tonnes per hectare
\end{itemize}
\item Weather:
\begin{itemize}
\item Daily, $0.25^{\circ}$ resolution gridded data
\item Precipitation
	\begin{itemize}
	\item Climate Hazards Group InfraRed Precipitation with Station data (CHIRPS)
	\end{itemize}
\item Temperature
	\begin{itemize}
	\item Berkeley Earth
	\end{itemize}
	\item[$\blacksquare$] Aggregation needed to conform with the yield data
\end{itemize}

@@

@@

\section*{}

\frame[allowframebreaks]{ 
\centering
\huge{Thank you for attention}
}

@@

\frame[allowframebreaks]{ 
\small
\frametitle{References}
\bibliographystyle{apa}
\bibliography{referencesFS}
}

\end{document}

>>>>

\begin{enumerate}
\item Arid and semi-arid (ASAL): bi-modal
	\begin{itemize}
	\item Short rains: March to May
	\item Long rains: October to December
	\end{itemize}
\item non-ASAL: uni-modal
	\begin{itemize}
	\item March to August
	\end{itemize}

@@

\begin{frame}\label{Approaches00}
\frametitle{Approach}

@@

\begin{frame}\label{Approaches01}
       \hspace{-0.8cm}  \textbf{NDMA Early Warning Phase\\ \hspace{-0.8cm} Classification}

@@

\vspace{-1.3cm}
    \begin{figure}
      \begin{columns}
        \column{.5\linewidth }
  \vspace{-1.8cm}        
        \column{.5\linewidth}
  \hspace{-2.6cm}  \includegraphics[width = 1.2\textwidth]{PrecNA.png}  %565*238
      \end{columns}
    \end{figure}

@@

%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
\section{Data}
\begin{frame}\label{Data}
\frametitle{Data}

\begin{itemize}
\item Maize yields
\begin{itemize}
\item source: Famine Early Warning Systems Network (FEWS NET)
\item County level, yearly, tonnes per hectare
\end{itemize}
\item Weather:
\begin{itemize}
\item Daily, $0.25^{\circ}$ resolution gridded data
\item Precipitation
	\begin{itemize}
	\item source: Climate Hazards Group InfraRed Precipitation with Station data (CHIRPS)
	\end{itemize}
\item Temperature
	\begin{itemize}
	\item source: Berkeley Earth
	\end{itemize}
	\item[$\blacksquare$] \textcolor{darkblue}{Aggregation needed to conform with the yield data}
	\end{itemize}

@@

\begin{columns}
\footnotesize
	\begin{column}{0.4\textwidth}

	\end{column}
	\begin{column}{0.15\textwidth}
  		$0.25^{\circ}$ grid \\ daily
	\end{column}
	\begin{column}{0.05\textwidth}
  			$\rightarrow$ \\ $\rightarrow$
	\end{column}
	\begin{column}{0.25\textwidth} 
   		county level \\  yearly
   	\end{column}
   		\begin{column}{0.4\textwidth} 
   		\end{column}
\end{columns}

@@

\section*{}
\frame[allowframebreaks]{ 
\centering
\huge{Thank you for attention}
}

@@

%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo

% 		---                	THE END       ---           ---

%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo

\newgeometry{top=10mm, left=10mm, right=10mm, bottom=10mm}

\frame[allowframebreaks, plain]{ 
\small
\frametitle{Precipitation and temperature measures considered}

\item Total precipitation over the rainy season\\
\item Coefficient of variation of the precipitation during the rainy season\\
\item Maximum length of dry spell during the rainy season (in number of days)\\
\item Number of dry spells during the rainy season: a dry spell defined as $4$ consecutive days without rain or more\footnotemark[1]\\
\item Number of dry spells during the rainy season: a dry spell defined as $10$ consecutive days without rain or more\footnotemark[1]\\
\item Number of dry spells during the rainy season: a dry spell defined as $20$ consecutive days without rain or more\footnotemark[1]\\

\footnotetext[1]{Threshold for a dry day was considered $1$mm.}
\end{frame}

\frame[allowframebreaks,plain]{ 
\small
\frametitle{Precipitation and temperature measures considered}

\item Average temperature during the rainy season\\
\item Standard deviation of temperature during the rainy season\\
\item Cumulative degree days during the rainy season (excluding the days when maximum temperature above $30^{\circ}$C or below $10^{\circ}$C\\
\item Number of heatwave days during the rainy season when max. temperature $>35^{\circ}$C
\\
\item Maximum daily precipitation  - to control for possible floods
\\
\item Sum of precipitation amount on days where precipitation is above $90^{th}$ percentile of precip. of the whole period\footnotemark[2]\\
\item Sum of precipitation amount on days where precipitation is above $95^{th}$ percentile of precip. of the whole period\footnotemark[3]\\
\end{itemize}
\footnotetext[2]{$90^{th}$ percentile was calculated for the subsample of wet days, that is the days where precipitation is above or equal to $1$mm.}
\footnotetext[3]{$95^{th}$ percentile was calculated for the subsample of wet days, that is the days where precipitation is above or equal to $1$mm.}
\end{frame}

\frame[allowframebreaks,plain]{ 
\small
\frametitle{Precipitation and temperature measures considered}

\begin{itemize}
\item Sum of precipitation amount on days where precipitation is above $99^{th}$ percentile of precip. of the whole period\footnotemark[4]\\
\item Number of days where precipitation is above $90^{th}$ percentile of precip. of the whole period\footnotemark[2]\\
\item Number of days where precipitation is above $95^{th}$ percentile of precip. of the whole period\footnotemark[3]\\

\item Number of days where precipitation is above $99^{th}$ percentile of precip. of the whole period\footnotemark[4]\\

\footnotetext[2]{$90^{th}$ percentile was calculated for the subsample of wet days, that is the days where precipitation is above or equal to $1$mm.}
\footnotetext[3]{$95^{th}$ percentile was calculated for the subsample of wet days, that is the days where precipitation is above or equal to $1$mm.}
\footnotetext[4]{ $99^{th}$ percentile was calculated for the subsample of wet days, that is the days where precipitation is above or equal to $1$mm.}
\end{frame}
\end{document}
